Ideal model selection is impossible

### 2014-10-23 Facticity/Facticity/paper.tex
best of both worlds proof

>>>>

\begin{proof}[Proof (combined)]
First note that there is a $c'$ such that 
\begin{equation}
	K(1^r 0  x) + c' \geq K(x) \label{eq:prelim1}
\end{equation}
for all $x$, since we can create a program that first runs the shortest program for $1^r 0 x$ and then strips the prefix $1^r 0$ from the result.

Define $\phi_{1^r0i}(x) = \psi_{i}(x)$, with $\phi_{j}(x) = \infty$ if $j$ does not contain a zero. Intuitively, any $\phi$-program is $r+1$ bits longer than the corresponding $\psi$-program. However, the used prefix function complicates this slightly. [TODO assume the prefix function to be convex.] But all we need is the bound
\begin{equation}\label{eq:prelim2}\begin{split}
K^\phi(x) &= \min \{ |\overline{1^r 0 \imath}| y : \phi_{1^r 0 i}(y) = x \}\\
&  \ge \min\{|1^r0\bar\imath y| : \phi_{1^r 0 i}(y) = x \}\qquad\tn{(using convexity of $\bar\cdot$)}\\
& = r+1 +\min\{|\bar\imath y| : \psi_i(y) = x \}\\
& = r+1+K^\psi(x).
\end{split}\end{equation}

We can now relate the complexity of $f$ under the two enumerations as follows:
\begin{align*}
K^\phi(f) &= \min\left\{ K^\phi(j) : \phi_j = f \right\}& \\
       &= \min\left\{ K^\phi(1^r0i) : \phi_{ri} = f \right\}& \\
       &\ge  \min\left\{ K^\phi(i) : \phi_{ri} = f \right\}-c'&\text{by~\eqref{eq:prelim1}}\\
       &\geq \min\left\{ K^\psi(i)  : \phi_{ri} = f \right\}+r+1-c'& \text{by \eqref{eq:prelim2}}\\
       &= \min\left\{ K^\psi(i) : \psi_{i} = f \right\} + r+1 -c'& \\
       &= K^\psi(f) + r + 1 - c'.
\end{align*}
The proof is completed by choosing $r=c+c'-1$.
\end{proof}
